---
title: "Positional accuracy - Analysis of sampling methods"
output: html_document
---
## Introduction 

This is an R Markdown scrip made to document the process of comparing various data sampling methods necessary for anlysing the positional accuracy OSM road network 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("//dataserver0.ciesin.columbia.edu/GlobalRoads/OSM_evaluation/Methods_Testing/Scripts/Functions")
source("basic_analysis.txt")
source("regional_analysis.txt")
source("urban_rural_analysis.txt")
source("match_data.txt")
source("sensitivity_analysis.txt")
source("sensitivity_analysis_correction.txt")
```

```{r, message=FALSE, warning=FALSE}

liberia_urban_rural_data_location <-'//dataserver0.ciesin.columbia.edu/GlobalRoads/OSM_evaluation/Methods_Testing/Outputs/Positional_accuracy/Sampling Schemes Testing/Random Points/Liberia/Multistage stratified'

guinea_urban_rural_data_location <- '//dataserver0.ciesin.columbia.edu/GlobalRoads/OSM_evaluation/Methods_Testing/Outputs/Positional_accuracy/Sampling Schemes Testing/Random Points/Guinea/Multistage stratified'

ghana_data_location <- '//dataserver0.ciesin.columbia.edu/GlobalRoads/OSM_evaluation/Methods_Testing/Outputs/Positional_accuracy/Multistage stratified/Ghana/input'

senegal_data_location <- '//dataserver0.ciesin.columbia.edu/GlobalRoads/OSM_evaluation/Methods_Testing/Outputs/Positional_accuracy/Multistage stratified/Senegal/input'
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(rgdal)
library(maptools)
library(raster)
library(rgeos)
library(classInt)
library(RColorBrewer)
library(RANN)
library(Matrix)
library(spdep)
library(plyr)
library(ggplot2)
library(gridExtra)
library(rmarkdown)
library(xtable)
library(Rlab)
```

## Versioning analysis

This part of the code checks the correlation between the number of versions of OSM road network features and positional accuracy. Road intersections were tagged with the average number of versions of 'parent' road segments. Also they were tagged with thier RMSE respective to coresponding intersection sampled on imagery.


```{r, echo=FALSE, message=FALSE, warning=FALSE}

##Read/Prepare Liberia##
keeps <- c("Name","MEAN_osmve","pointRMSE","Type")
ge_data_urban_rural <- readOGR(liberia_urban_rural_data_location,'ge_data',verbose=FALSE)
osm_data_urban_rural <- readOGR(liberia_urban_rural_data_location,'osm_data',verbose=FALSE)
a<-match_data(ge_data_urban_rural,osm_data_urban_rural)
new_a <- a[,(names(a) %in% keeps)]


##Read/Prepare Guinea##

ge_data_urban_rural <- readOGR(guinea_urban_rural_data_location,'ge_data',verbose=FALSE)
osm_data_urban_rural <- readOGR(guinea_urban_rural_data_location,'osm_data',verbose=FALSE)
b<-match_data(ge_data_urban_rural,osm_data_urban_rural)
new_b <- b[,(names(b) %in% keeps)]

##Read/Prepare Ghana##
setwd(ghana_data_location)
admin_units <- readOGR(ghana_data_location,'admin_units_tagged',verbose=FALSE)
admin_units_proj <- spTransform(admin_units, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data_urban_rural <- readOGR(ghana_data_location,'intersections_select',verbose=FALSE)
ge_data_urban_rural <-readOGR(dsn="sampled_intersections.kml",layer="Temporary Places")
ge_data_urban_rural<-spTransform(ge_data_urban_rural, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data_urban_rural <- intersect(osm_data_urban_rural, admin_units_proj)
colnames(osm_data_urban_rural@data)[60] <- "Type"
c<-match_data(ge_data_urban_rural,osm_data_urban_rural)
new_c <- c[,(names(c) %in% keeps)]

##Read/Prepare Senegal##

setwd(senegal_data_location)
admin_units <- readOGR(senegal_data_location,'admin_units_tagged',verbose=FALSE)
admin_units_proj <- spTransform(admin_units, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data_urban_rural <- readOGR(senegal_data_location,'intersections_select',verbose=FALSE)
ge_data_urban_rural <-readOGR(dsn="sampled_intersections.kml",layer="Temporary Places")
ge_data_urban_rural<-spTransform(ge_data_urban_rural, CRS("+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +units=m +no_defs"))
osm_data_urban_rural <- intersect(osm_data_urban_rural, admin_units_proj)
colnames(osm_data_urban_rural@data)[60] <- "Type"
d<-match_data(ge_data_urban_rural,osm_data_urban_rural)
new_d <- d[,(names(d) %in% keeps)]
```

```{r, include=FALSE}
countries = c("Liberia", "Guinea", "Ghana", "Senegal","Global-U","Global-R","Global-U-R") 
coeff_all_values = c(0, 0, 0, 0, 0, 0, 0)
all_count = c(0, 0, 0, 0, 0, 0, 0)
coeff_subset = c(0, 0, 0, 0, 0, 0, 0) 
subset_count = c(0, 0, 0, 0, 0, 0, 0)
correlation = data.frame(countries, coeff_all_values, all_count, coeff_subset, subset_count)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}

#Liberia

analysis_data <- new_a
correlation$coeff_all_values[1] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[1] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[1] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[1]<- length(analysis_data_filtered@data$MEAN_osmve)

#Guinea

analysis_data <- new_b
correlation$coeff_all_values[2] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[2] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[2] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[2]<- length(analysis_data_filtered@data$MEAN_osmve)

#Ghana

analysis_data <- new_c
correlation$coeff_all_values[3] <-cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[3] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[3] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[3]<- length(analysis_data_filtered@data$MEAN_osmve)

#Senegal

analysis_data <- new_d
correlation$coeff_all_values[4] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[4] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[4] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[4]<- length(analysis_data_filtered@data$MEAN_osmve)

#Global - Urban Data Only

analysis_data <- rbind(new_a,new_b,new_c,new_d)
analysis_data <- analysis_data[analysis_data@data$Type=="urban",]
correlation$coeff_all_values[5] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[5] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[5] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[5]<- length(analysis_data_filtered@data$MEAN_osmve)

#Global - Rural Data Only

analysis_data <- rbind(new_a,new_b,new_c,new_d)
analysis_data <- analysis_data[analysis_data@data$Type=="rural",]
correlation$coeff_all_values[6] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[6] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[6] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[6]<- length(analysis_data_filtered@data$MEAN_osmve)

#Global - Urban - Rurla Data

analysis_data <- rbind(new_a,new_b,new_c,new_d)
correlation$coeff_all_values[7] <- cor(analysis_data@data$MEAN_osmve, analysis_data@data$pointRMSE)
analysis_data_filtered <- analysis_data[analysis_data@data$MEAN_osmve>=3,]
correlation$coeff_subset[7] <- cor(analysis_data_filtered@data$MEAN_osmve, analysis_data_filtered@data$pointRMSE)
correlation$all_count[7] <- length(analysis_data@data$MEAN_osmve)
correlation$subset_count[7]<- length(analysis_data_filtered@data$MEAN_osmve)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("C:/Users/Bogdan/Desktop/Regressions_Scripts/Complete_SHP")
write.table(correlation, file = "foo.csv", sep = ",")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
data_location <- "C:/Users/Bogdan/Desktop/Regressions_Scripts/Complete_SHP"
setwd(data_location)
analysis_data <- rbind(new_a,new_b,new_c,new_d)
png('versioning_correlation.png',width = 10, height= 7, units = 'in' , res = 300)
ggplot(analysis_data@data,aes(MEAN_osmve,pointRMSE))+geom_point(color="blue")+xlab("Number of versions (-)") + ylab("RMSE (m)")+geom_smooth(data=analysis_data@data,aes(MEAN_osmve,pointRMSE),method=lm,se=FALSE)
dev.off()
```("Relation between RMSE and Numberof version in all points sampled using the stratified sampling scheme")
